\papertitle

### 2024-09-12 src/tex/ms.tex
Latest version

\begin{figure*}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure1.pdf}}
    \includegraphics[width=\textwidth]{schematic.pdf}
    \caption{
        A schematic diagram of the Bayesian regression method described in this work, running from our simulations through the sampling of displacement, variance and covariance estimation and final the sampling process to give the marginal posterior distribution for $\D$.}
    \label{fig:schematic}
\end{figure*}

@@

\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure1.pdf}}
    \includegraphics[width=\columnwidth]{glswlsols.pdf}
    \script{glswlsols.py}
    \caption{
        Example distributions of estimated self-diffusion coefficients, $\Dest$, calculated using (a) ordinary least squares (OLS), (b) weighted least squares (WLS), and (c) generalised least squares (GLS),
        from MSD data from \num{4096} individual simulations of \num{128} particles undergoing a \SI{128}{step} 3D lattice random walk, with a step size chosen so that the true diffusion coefficient $\D = 1$.
        In each panel, the grey curve shows the best-fit normal distribution for the simulation data, the upper horizontal bar shows the standard deviation of this distribution, and the lower horizontal bar shows the average estimated standard distribution given by the analytical expression for $\sigma[\prob{\Dest}]$ for each regression method.}
    \label{fig:glswlsols}
\end{figure}

@@

\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure2.pdf}}
    \includegraphics[width=\columnwidth]{msd.pdf}
    \script{msd.py}
    \caption{
        Comparison of the numerical variance in observed MSD from multiple replica simulations and the estimated variance in observed MSD given by rescaling the variance in observed squared displacements (Eqn.~\ref{equ:varestMSD}).
        Panel (a) shows the mean observed MSD from \num{4096} simulations of \num{128} particles undergoing a 3D lattice random walk of \num{128} steps per particle, with error bars of $\pm2\sigma[\oMSDi]$.
        Panel (b) shows the MSD from just one simulation, with error bars of $\pm2\widehat{\sigma}[\oMSDi]$, obtained via Eqn.~\ref{equ:varestMSD}.
        Panel (c) plots the numerical variance against the estimated variance from a single simulation as a function of timestep $i$.
        %Raw simulation data~\cite{mccluskey_zenodo_2022} and scripts~\cite{mccluskey_github_2022} to generate this figure are available under CC BY 4.0/MIT licences.
    }
    \label{fig:msd}
\end{figure}

@@

To illustrate the complete numerical procedure for deriving the estimated covariance matrix, $\widehat{\mathbf{\Sigma}}$, we present in Fig.~\ref{fig:covariances} the MSD covariance matrix for \num{4096} random-walk simulations, as described above, at three differing levels of approximation:
the numerically converged covariance matrix, $\bm{\Sigma}$, computed using the data from all \num{4096} simulations (Fig.~\ref{fig:covariances}a);
the corresponding analytical covariance matrix, $\mathbf{\Sigma^\prime}$, derived in the SI (Fig.~\ref{fig:covariances}b); and the average estimated covariance matrix obtained by parametrising Eqn.~\ref{equ:cvv} using smoothed variances estimated from individual simulation trajectories, and averaging over the resulting set of all \num{4096} matrices (Fig.~\ref{fig:covariances}c).

% \begin{figure}
%     \centering
%     % \resizebox{\columnwidth}{!}{\includegraphics*{figure3.pdf}}
%     \includegraphics[width=\columnwidth]{covariances.pdf}
%     \script{covariances.py}
%     \caption{
%         (a) The numerical MSD covariance matrix $\bm{\Sigma}$ calculated using MSD data from \num{4096} simulations of \num{128} particles undergoing a 3D lattice random walk of \num{128} steps per particle.
%         (b) The analytical MSD covariance matrix $\bm{\Sigma^\prime}$ (Eqn.~\ref{equ:cvv_SI}).
%         (c) The MSD covariance matrix obtained applying the numerical scheme described in the main text to each individual random walk simulation, averaged over all \num{4096} such simulations.
%         Colour bars in (a--c) show the covariance, $\Sigma\left[\oMSDi, \oMSDj\right]$.
%         The off-diagonal panels show scale plots, computed as per-element ratios between pairs of covariance matrices (a--c).
%         %Raw simulation data~\cite{mccluskey_zenodo_2022} and scripts~\cite{mccluskey_github_2022} to generate this figure are available under CC BY 4.0/MIT licences.
%     }
%     \label{fig:covariances}
% \end{figure}

@@

\begin{figure*}[ht!]
    \centering
    % \resizebox{\textwidth}{!}{\includegraphics*{figure4.pdf}}
    \includegraphics[width=\textwidth]{random_walk.pdf}
    \script{random_walk.py}
    \caption{
        (a) Observed MSD from a single simulation of 128 particles undergoing a 3D-lattice random walk of 128 steps per particle (dark line).
        The green shading shows the corresponding posterior distribution $\prob{\model|\oMSD}$ of linear models compatible with the observed MSD data $\oMSD$, calculated using the scheme described in the main text.
        The variegated shading indicates compatibility intervals of \SIlist[list-final-separator = {, and }]{1;2;3}{\sigma}$[\prob{\model|\oMSD}]$.
        (b) The marginal posterior distribution $\prob{\Dest|\oMSD}$ obtained from the posterior distribution of linear models in (a).
        The mean of this distribution gives the point estimate $\Dest$ for this simulation input data.
        The blue horizontal bar shows an interval of one standard deviation in $\prob{\Dest|\oMSD}$.
        (c) Probability distribution of point-estimates $\prob{\Dest}$ obtained from \num{4096} individual random-walk simulations.
        Each simulation has been analysed as in (a) and (b) to yield a single corresponding point estimate $\Dest$.
        The grey line shows the distribution of point estimates, $\prob{\Dest_\mathrm{num}}$, obtained using Bayesian regression with a mean vector and numerical covariance matrix derived from the complete dataset of all \num{4096} simulations.
        The pink horizontal bar shows an interval of one standard deviation in $\prob{\Dest}$.
        (d) Probability distribution of estimated variances, $\varest{\Dest}$, for individual random-walk simulations, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
    } 
    \label{fig:random_walk}
\end{figure*}

@@

% \begin{figure}[tb]
%     \centering
%     % \resizebox{\columnwidth}{!}{\includegraphics*{figure5.pdf}}
%     \includegraphics[width=\columnwidth]{diffusion.pdf}
%     \script{diffusion.py}
%     \caption{
%       (a) Probability distribution of point estimates $\prob{\Dest}$ for \num{480} effective simulations of LLZO (orange histogram).
%       The grey line shows the distribution $\prob{\Dest_\mathrm{num}}$ obtained using Bayesian regression with the complete LLZO dataset as input.
%       The pink bar shows an interval of one standard deviation $\sigma[\prob{\Dest}]$.
%       (b) Probability distribution of estimated variances, $\varest{\Dest}$, for individual LLZO effective simulations, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
%       %Raw simulation data~\cite{mccluskey_zenodo_2022} and scripts~\cite{mccluskey_github_2022} to generate this figure are available under CC BY 4.0/MIT licences. 
%     }
%     \label{fig:diffusion}
% \end{figure}

@@

\begin{figure}[htb]
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure6.pdf}}
    \includegraphics[width=\columnwidth]{stat_eff.pdf}
    \script{stat_eff.py}
    \caption{
      Scaling of $\var{\Dest}$ with simulation size for OLS (pink), WLS (blue), our approximate Bayesian regression method (green), and GLS (orange).
      (a) Scaling versus number of mobile particles, $N_\mathrm{atoms}$.
      (b) Scaling versus total simulation time, $t_\mathrm{max}$.
      Solid lines show fitted power law relationships for each dataset.
      The WLS and GLS data are obtained using numerically determined variances and covariance, respectively, from a set of \num{512} repeat simulations for each combination of $N_\mathrm{atoms}$ and $t_\mathrm{max}$.
    }
    \label{fig:stat_eff}
\end{figure}

@@

\subsection{Numerical implementation in KINISI}
\label{sec:implementation}
We have implemented the approximate Bayesian estimation method described in the main text in the open-source Python package \textsc{kinisi}~\cite{mccluskey_kinisi_2022}, under the MIT licence.
Throughout this work, kinisi-[INSERT VERSION NUMBER] was used for all analyses.

@@

\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure1.pdf}}
    \includegraphics[width=\columnwidth]{pyblock.pdf}
    \script{pyblock.py}
    \caption{Comparison of the distribution of $\Dest$ (a \& c) and the estimated variances (b \& d) from 4096 individual random walk simulations using variances approximated by Eqn.~\ref{equ:varestMSD} (a \& b), from block averaging (c \& d).}
    \label{fig:pyblock}
\end{figure}

@@

This bias and skew arise from our use of estimated variances $\varest{\oMSDi}$ when parametrising the model covariance matrix $\bm{\Sigma^\prime}$.
Fig.~\ref{fig:true_cov} presents equivalent results for $\prob{\Dest}$ and $\prob{\varest{\Dest}}$ for the same \num{4096} individual simulations, but calculated using a numerical covariance matrix, $\bm{\Sigma}_\mathrm{num}$ derived from all \num{4096} observed MSDs.
The resulting distribution $\prob{\varest{\Dest}}$ (Fig.~\ref{fig:true_cov}b) is no longer biased or skewed.
Furthermore, the distribution $\prob{\Dest}$ agrees even more closely with the numerically converged distribution obtained when combining data from all \num{4096} simulations (Fig~\ref{fig:true_cov}a), contrasting with the results presented in Fig.~\ref{fig:random_walk}b, where our approximate Bayesian regression scheme yields a slightly broadened distribution due to the use of the long-time limit in the derivation of the analytical form for $\bm{\Sigma^\prime}$.
\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure7.pdf}}
    \includegraphics[width=\columnwidth]{true_cov.pdf}
    \script{true_cov.py}
    \caption{
        (a) Probability distribution of point-estimates $\prob{\Dest}$ obtained from \num{4096} individual random-walk simulations, using the numerical covariance matrix $\bm{\Sigma}_\mathrm{num}$.
        Each simulation has been analysed as in Fig.~~\ref{equ:observed_msd}(a) and (b) to yield a single corresponding point estimate $\Dest$.
        The grey line shows the distribution of point estimates, $\prob{\Dest_\mathrm{num}}$, obtained using Bayesian regression with a mean vector and numerical covariance matrix derived from the complete dataset of all \num{4096} simulations.
        The pink horizontal bar shows an interval of one standard deviation in $\prob{\Dest}$.
        (b) Probability distribution of estimated variances, $\varest{\Dest}$, for individual random-walk simulations, using the numerical covariance matrix $\bm{\Sigma}_\mathrm{num}$, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
        }
    \label{fig:true_cov}
\end{figure}

@@

In Fig.~\ref{fig:glswlsols}, it is shown that for a 3D lattice random walk the heteroscedastic and correlated nature of the data requires generalised least squares to optimally estimate the true ensemble-average MSD, and therefore estimate $\D$. 
This is also true for the real materials, such as the \ce{Li7La3Zr2O12} (LLZO) investigated by classical molecular dynamics simulation in this work (Fig.~\ref{fig:glswlsols_llzo}).
Once again, GLS (or, indeed, the Bayesian regression equivalent, shown in Fig.~\ref{fig:diffusion}) offers both the most statistically efficient estimation of $\D$ and is required to obtain an accruate estimate of the statistical uncertainty in $\D$ from a single simulation. 
% \begin{figure}
%     \centering
%     % \resizebox{\columnwidth}{!}{\includegraphics*{figure1.pdf}}
%     \includegraphics[width=\columnwidth]{glswlsols_llzo.pdf}
%     \script{glswlsols_llzo.py}
%     \caption{
%         Example distributions of estimated self-diffusion coefficients, $\Dest$, calculated using (a) ordinary least squares (OLS), (b) weighted least squares (WLS), and (c) generalised least squares (GLS),
%         from MSD data from \num{512} effective simulations of LLZO of \SI{\sim 25}{\pico\second} with 56 lithium ions.
%         In each panel, the grey curve shows the best-fit normal distribution for the simulation data, the upper horizontal bar shows the standard deviation of this distribution, and the lower horizontal bar shows the average estimated standard distribution given by the analytical expression for $\sigma[\prob{\Dest}]$ for each regression method.}
%     \label{fig:glswlsols_llzo}
% \end{figure}

>>>>

\begin{figure*}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure1.pdf}}
    \includegraphics[width=\textwidth]{schematic.pdf}
    \caption{
        A schematic diagram of the Bayesian regression method described in this work, from running simulations through the sampling of displacement, variance and covariance estimation and final the sampling process to give the marginal posterior distribution for $\D$.}
    \label{fig:schematic}
\end{figure*}

@@

\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure2.pdf}}
    \includegraphics[width=\columnwidth]{glswlsols.pdf}
    \script{glswlsols.py}
    \caption{
        Example distributions of estimated self-diffusion coefficients, $\Dest$, calculated using (a) ordinary least squares (OLS), (b) weighted least squares (WLS), and (c) generalised least squares (GLS),
        from MSD data from \num{4096} individual simulations of \num{128} particles undergoing a \SI{128}{step} 3D lattice random walk, with a step size chosen so that the true diffusion coefficient $\D = 1$.
        In each panel, the grey curve shows the best-fit normal distribution for the simulation data, the upper horizontal bar shows the standard deviation of this distribution, and the lower horizontal bar shows the average estimated standard distribution given by the analytical expression for $\sigma[\prob{\Dest}]$ for each regression method.}
    \label{fig:glswlsols}
\end{figure}

@@

\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure3.pdf}}
    \includegraphics[width=\columnwidth]{msd.pdf}
    \script{msd.py}
    \caption{
        Comparison of the numerical variance in observed MSD from multiple replica simulations and the estimated variance in observed MSD given by rescaling the variance in observed squared displacements (Eqn.~\ref{equ:varestMSD}).
        Panel (a) shows the mean observed MSD from \num{4096} simulations of \num{128} particles undergoing a 3D lattice random walk of \num{128} steps per particle, with error bars of $\pm2\sigma[\oMSDi]$.
        Panel (b) shows the MSD from just one simulation, with error bars of $\pm2\widehat{\sigma}[\oMSDi]$, obtained via Eqn.~\ref{equ:varestMSD}.
        Panel (c) plots the numerical variance against the estimated variance from a single simulation as a function of timestep $i$.
        %Raw simulation data~\cite{mccluskey_zenodo_2022} and scripts~\cite{mccluskey_github_2022} to generate this figure are available under CC BY 4.0/MIT licences.
    }
    \label{fig:msd}
\end{figure}

@@

To illustrate the complete numerical procedure for deriving the estimated covariance matrix, $\widehat{\mathbf{\Sigma}}$, we present in Fig.~\ref{fig:covariances} the MSD covariance matrix for \num{4096} random-walk simulations, as described above, at three differing levels of approximation:
the numerically converged covariance matrix, $\bm{\Sigma}$, computed using the data from all \num{4096} simulations (Fig.~\ref{fig:covariances}a);
the corresponding analytical covariance matrix, $\mathbf{\Sigma^\prime}$, derived in the SI (Fig.~\ref{fig:covariances}b); and the average estimated covariance matrix obtained by parametrising Eqn.~\ref{equ:cvv} using calculated variances estimated from individual simulation trajectories, and averaging over the resulting set of all \num{4096} matrices (Fig.~\ref{fig:covariances}c).

\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure4.pdf}}
    \includegraphics[width=\columnwidth]{covariances.pdf}
    \script{covariances.py}
    \caption{
        (a) The numerical MSD covariance matrix $\bm{\Sigma}$ calculated using MSD data from \num{4096} simulations of \num{128} particles undergoing a 3D lattice random walk of \num{128} steps per particle.
        (b) The analytical MSD covariance matrix $\bm{\Sigma^\prime}$ (Eqn.~\ref{equ:cvv_SI}).
        (c) The MSD covariance matrix obtained applying the numerical scheme described in the main text to each individual random walk simulation, averaged over all \num{4096} such simulations.
        Colour bars in (a--c) show the covariance, $\Sigma\left[\oMSDi, \oMSDj\right]$.
        The off-diagonal panels show scale plots, computed as per-element ratios between pairs of covariance matrices (a--c).
        %Raw simulation data~\cite{mccluskey_zenodo_2022} and scripts~\cite{mccluskey_github_2022} to generate this figure are available under CC BY 4.0/MIT licences.
    }
    \label{fig:covariances}
\end{figure}

@@

\begin{figure*}[ht!]
    \centering
    % \resizebox{\textwidth}{!}{\includegraphics*{figure5.pdf}}
    \includegraphics[width=\textwidth]{random_walk.pdf}
    \script{random_walk.py}
    \caption{
        (a) Observed MSD from a single simulation of 128 particles undergoing a 3D-lattice random walk of 128 steps per particle (dark line).
        The green shading shows the corresponding posterior distribution $\prob{\model|\oMSD}$ of linear models compatible with the observed MSD data $\oMSD$, calculated using the scheme described in the main text.
        The variegated shading indicates compatibility intervals of \SIlist[list-final-separator = {, and }]{1;2;3}{\sigma}$[\prob{\model|\oMSD}]$.
        (b) The marginal posterior distribution $\prob{\Dest|\oMSD}$ obtained from the posterior distribution of linear models in (a).
        The mean of this distribution gives the point estimate $\Dest$ for this simulation input data.
        The blue horizontal bar shows an interval of one standard deviation in $\prob{\Dest|\oMSD}$.
        (c) Probability distribution of point-estimates $\prob{\Dest}$ obtained from \num{4096} individual random-walk simulations.
        Each simulation has been analysed as in (a) and (b) to yield a single corresponding point estimate $\Dest$.
        The grey line shows the distribution of point estimates, $\prob{\Dest_\mathrm{num}}$, obtained using Bayesian regression with a mean vector and numerical covariance matrix derived from the complete dataset of all \num{4096} simulations.
        The pink horizontal bar shows an interval of one standard deviation in $\prob{\Dest}$.
        (d) Probability distribution of estimated variances, $\varest{\Dest}$, for individual random-walk simulations, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
    } 
    \label{fig:random_walk}
\end{figure*}

@@

\begin{figure}[tb]
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure6.pdf}}
    \includegraphics[width=\columnwidth]{diffusion.pdf}
    \script{diffusion.py}
    \caption{
      (a) Probability distribution of point estimates $\prob{\Dest}$ for \num{480} effective simulations of LLZO (orange histogram).
      The grey line shows the distribution $\prob{\Dest_\mathrm{num}}$ obtained using Bayesian regression with the complete LLZO dataset as input.
      The pink bar shows an interval of one standard deviation $\sigma[\prob{\Dest}]$.
      (b) Probability distribution of estimated variances, $\varest{\Dest}$, for individual LLZO effective simulations, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
      %Raw simulation data~\cite{mccluskey_zenodo_2022} and scripts~\cite{mccluskey_github_2022} to generate this figure are available under CC BY 4.0/MIT licences. 
    }
    \label{fig:diffusion}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure7.pdf}}
    \includegraphics[width=\columnwidth]{stat_eff.pdf}
    \script{stat_eff.py}
    \caption{
      Scaling of $\var{\Dest}$ with simulation size for OLS (pink), WLS (blue), our approximate Bayesian regression method (green), and GLS (orange).
      (a) Scaling versus number of mobile particles, $N_\mathrm{atoms}$.
      (b) Scaling versus total simulation time, $t_\mathrm{max}$.
      Solid lines show fitted power law relationships for each dataset.
      The WLS and GLS data are obtained using numerically determined variances and covariance, respectively, from a set of \num{512} repeat simulations for each combination of $N_\mathrm{atoms}$ and $t_\mathrm{max}$.
    }
    \label{fig:stat_eff}
\end{figure}

@@

\subsection{Numerical implementation in KINISI}
\label{sec:implementation}
We have implemented the approximate Bayesian estimation method described in the main text in the open-source Python package \textsc{kinisi}~\cite{mccluskey_kinisi_2022}, under the MIT licence.
Throughout this work, \textsc{kinisi}-1.1.0 was used for all analyses.

@@

\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure8.pdf}}
    \includegraphics[width=\columnwidth]{pyblock.pdf}
    \script{pyblock.py}
    \caption{Comparison of the distribution of $\Dest$ (a \& c) and the estimated variances (b \& d) from 4096 individual random walk simulations using variances approximated by Eqn.~\ref{equ:varestMSD} (a \& b), from block averaging (c \& d).}
    \label{fig:pyblock}
\end{figure}

\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure8.pdf}}
    \includegraphics[width=\columnwidth]{msd_blocking.pdf}
    \script{msd_blocking.py}
    \caption{Comparison of the distribution of $\Dest$ (a \& c) and the estimated variances (b \& d) from 4096 individual random walk simulations using variances approximated by Eqn.~\ref{equ:varestMSD} (a \& b), from block averaging (c \& d).}
    \label{fig:msd_blocking}
\end{figure}

@@

This bias and skew arise from our use of estimated variances $\varest{\oMSDi}$ when parametrising the model covariance matrix $\bm{\Sigma^\prime}$.
Fig.~\ref{fig:true_cov} presents equivalent results for $\prob{\Dest}$ and $\prob{\varest{\Dest}}$ for the same \num{4096} individual simulations, but calculated using a numerical covariance matrix, $\bm{\Sigma}_\mathrm{num}$ derived from all \num{4096} observed MSDs.
The resulting distribution $\prob{\varest{\Dest}}$ (Fig.~\ref{fig:true_cov}b) is no longer biased or skewed.
Furthermore, the distribution $\prob{\Dest}$ agrees even more closely with the numerically converged distribution obtained when combining data from all \num{4096} simulations (Fig~\ref{fig:true_cov}a), contrasting with the results presented in Fig.~\ref{fig:random_walk}b, where our approximate Bayesian regression scheme yields a slightly broadened distribution due to the use of the long-time limit in the derivation of the analytical form for $\bm{\Sigma^\prime}$.
\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure9.pdf}}
    \includegraphics[width=\columnwidth]{true_cov.pdf}
    \script{true_cov.py}
    \caption{
        (a) Probability distribution of point-estimates $\prob{\Dest}$ obtained from \num{4096} individual random-walk simulations, using the numerical covariance matrix $\bm{\Sigma}_\mathrm{num}$.
        Each simulation has been analysed as in Fig.~~\ref{equ:observed_msd}(a) and (b) to yield a single corresponding point estimate $\Dest$.
        The grey line shows the distribution of point estimates, $\prob{\Dest_\mathrm{num}}$, obtained using Bayesian regression with a mean vector and numerical covariance matrix derived from the complete dataset of all \num{4096} simulations.
        The pink horizontal bar shows an interval of one standard deviation in $\prob{\Dest}$.
        (b) Probability distribution of estimated variances, $\varest{\Dest}$, for individual random-walk simulations, using the numerical covariance matrix $\bm{\Sigma}_\mathrm{num}$, compared to the true sample variance (pink vertical line) $\var{\Dest}$.
        }
    \label{fig:true_cov}
\end{figure}

@@

In Fig.~\ref{fig:glswlsols}, it is shown that for a 3D lattice random walk the heteroscedastic and correlated nature of the data requires generalised least squares to optimally estimate the true ensemble-average MSD, and therefore estimate $\D$. 
This is also true for the real materials, such as the \ce{Li7La3Zr2O12} (LLZO) investigated by classical molecular dynamics simulation in this work (Fig.~\ref{fig:glswlsols_llzo}).
Once again, GLS (or, indeed, the Bayesian regression equivalent, shown in Fig.~\ref{fig:diffusion}) offers both the most statistically efficient estimation of $\D$ and is required to obtain an accruate estimate of the statistical uncertainty in $\D$ from a single simulation. 
\begin{figure}
    \centering
    % \resizebox{\columnwidth}{!}{\includegraphics*{figure10.pdf}}
    \includegraphics[width=\columnwidth]{glswlsols_llzo.pdf}
    \script{glswlsols_llzo.py}
    \caption{
        Example distributions of estimated self-diffusion coefficients, $\Dest$, calculated using (a) ordinary least squares (OLS), (b) weighted least squares (WLS), and (c) generalised least squares (GLS),
        from MSD data from \num{512} effective simulations of LLZO of \SI{\sim 25}{\pico\second} with 56 lithium ions.
        In each panel, the grey curve shows the best-fit normal distribution for the simulation data, the upper horizontal bar shows the standard deviation of this distribution, and the lower horizontal bar shows the average estimated standard distribution given by the analytical expression for $\sigma[\prob{\Dest}]$ for each regression method.}
    \label{fig:glswlsols_llzo}
\end{figure}
